\Large The state learner -- a super learner for right-censored data

### 2025-01-13 manuscript/manuscript.tex
updated manuscript and appendix to late fixes

We introduce our notation and framework in
Section~\ref{sec:framework}. In Section~\ref{sec:super-learning} we define
general super learning for right-censored data.
Section~\ref{sec:super-learner-simple} introduces the state learner, and
Section~\ref{sec:theor-results-prop} provides theoretical guarantees. In
Section~\ref{sec:targeted-learning} we discuss the use of the state learner in
the context of targeted learning. We report results of our numerical experiments
in Section~\ref{sec:numer-exper} and analyse a prostate cancer data set in
Section~\ref{sec:real-data-appl}. Section~\ref{sec:discussion} contains a
discussion of the merits and limitations of our proposal.
Appendices~\ref{sec:proof-proposition} and~\ref{sec:state-learner-with} contain
proofs. An implementation of the state learner is available at
\url{https://github.com/amnudn/statelearner} along with codes for reproducing
our numerical experiments.

@@

\begin{proposition}
  \label{prop:stric-prop}
  If \(P_0\in\mathcal{P}\) then
  \begin{equation*}
    F_0 = \argmin_{F \in \mathcal{H}_{\mathcal{P}}} P_0{[\bar{B}_\tau(F, \blank)]},
  % F^* = \argmin_{(\Lambda_1,\Lambda_2,\Gamma) \in \mathcal{M}_{\tau}\otimes\mathcal{M}_{\tau}\otimes\mathcal{M}_{\tau}} P_0{[\bar B_\tau(\phi_{(\Lambda_1,\Lambda_2,\Gamma)}, \blank)]},
  \end{equation*}
  \( H \)-almost surely for any \( j\in \{-1,0,1,2\} \) and almost any
  \( t \in [0, \tau]\).
\end{proposition}
\begin{proof}
  See Appendix~\ref{sec:proof-proposition}.
\end{proof}

@@

\begin{corollary}
  \label{cor:oracle-prop}
  For all \(P_0\in\mathcal{P}\), \( n \in \N \), \( k \in \{1, \dots, K\} \),
  and $\delta>0$,
  \begin{align*}
    \E_{P_0}{\left[ \Vert \hat{\phi}_n(\data_n^{-k}) - F_0 \Vert_{P_0}^2 \right]}
    & \leq (1 + 2\delta)
      \E_{P_0}{\left[ \Vert \tilde{\phi}_n(\data_n^{-k}) - F_0 \Vert_{P_0}^2 \right]}
    \\
    & \quad
      + (1+ \delta) 16   K \tau
      \left(
      13 + \frac{12}{\delta}
      \right)
      \frac{\log(1 + |\mathcal{F}_n|)}{n}.
  \end{align*}
\end{corollary}
\begin{proof}
  See Appendix~\ref{sec:proof-proposition}.
\end{proof}

@@

\begin{corollary}
  \label{cor:asymp-cons}
  Assume that \( |\mathcal{F}_n| = \bigO(n^q)\), for some \( q \in \N \) and
  that there exists a sequence \( \phi_n \in \mathcal{F}_n \), \( n \in \N \),
  such that
  \( \E_{P_0}{\left[ \Vert \phi_n(\data_n^{-k}) - F_{0} \Vert_{P_0}^2 \right]} =
  \bigO(n^{-\alpha}) \), for some \( \alpha\leq 1 \).
  \begin{enumerate}[label=(\alph*)]
  \item If $\alpha=1$ then
    \( \E_{P_0}{\left[ \Vert \hat{\phi}_n(\data_n^{-k}) - F_0 \Vert_{P_0}^2
      \right]} = \bigO(\log(n)n^{-1}) \).
  \item If $\alpha<1$ then
    \( \E_{P_0}{\left[ \Vert \hat{\phi}_n(\data_n^{-k}) - F_0 \Vert_{P_0}^2 \right]} =
    \bigO(n^{-\alpha}) \).
  \end{enumerate}
\end{corollary}
\begin{proof}
  See Appendix~\ref{sec:proof-proposition}.
\end{proof}

\subsection{Transience of the second order remainder structure}

@@

@@

\section{Theoretical guarantees for the state learner}
\label{sec:proof-proposition}

In this section we provide proofs of the results stated in
Section~\ref{sec:theor-results-prop}.

Define
\( \bar{B}_{\tau,0}(F, o) = \bar{B}_{\tau}(F, o) - \bar{B}_{\tau}(F_0, o) \) and
\( R_{0}(F) = P_0{[\bar{B}_{\tau,0}(F, \blank)]} \).
\begin{lemma}
  \label{lemma:norm}
  \( R_{0}(F) = \Vert F - F_0 \Vert_{P_0}^2 \), where \( \Vert \blank \Vert_{P_0}\) is defined
  in equation~(\ref{eq:norm}).
\end{lemma}
\begin{proof}[Proof]
  For any \( t \in [0, \tau] \) and \( j\in \{-1,0,1,2\} \) we have
  \begin{align*}
    & \E_{P_0}{\left[ (F(t, j, X) - \1{\{\eta(t) = j \}})^2 \right]}
    \\
    & =    \E_{P_0}{\left[ (F(t, j, X) - F_0(t, j, X) + F_0(t, j, X) - \1{\{\eta(t) = j
      \}})^2 \right]}
    \\
    & =    \E_{P_0}{\left[ (F(t, j, X) - F_0(t, j, X))^2\right]}
      + \E_{P_0}{\left[ (F_0(t, j, X) - \1{\{\eta(t) = j \}})^2\right]}
    \\
    & \quad
      + 2\E_{P_0}{\left[ (F(t, j, X) - F_0(t, j, X))(F_0(t, j, X) - \1{\{\eta(t) = j
      \}})\right]}
    \\
    & =    \E_{P_0}{\left[ (F(t, j, X) - F_0(t, j, X))^2\right]}
      + \E_{P_0}{\left[ (F_0(t, j, X) - \1{\{\eta(t) = j \}})^2\right]},
  \end{align*}
  where the last equality follows from the tower property. Hence, using Fubini,
  we have
  \begin{equation*}
    P{[\bar{B}_{\tau}(F, \blank)]}
    = \Vert F - F_0 \Vert_{P_0}^2 + P_0{[\bar{B}_{\tau}(F_0, \blank)]}.
  \end{equation*}
\end{proof}

@@

Recall that $\mathcal{H}_{\mathcal{P}}$ denote the function space consisting of
all conditional state occupation probability functions for some measure
\( P \in \mathcal{P} \).

@@

\section{The state learner with targeted learning}
\label{sec:state-learner-with}

In this section show that a product structure is preserved when an estimator
$\bar\Psi(\hat{F}_n, \hat{H}_n)$ is used instead of
$\tilde\Psi(\hat{\Lambda}_n, \hat{\Gamma}_n, \hat{H}_n)$.

\begin{proof}[Proof of Proposition~\ref{prop:dr-structure}]
  For notational convenience we suppress \( X \) in the following. The final
  result can be obtained by adding the argument \( X \) to all functions and
  averaging. We use the relations from equation~(\ref{eq:7}) to write
  \begingroup %
  \allowdisplaybreaks
    \begin{align*}
      & \int_0^{\tau} w(s) 
        \left\{
        \Gamma(s) - \hat{\Gamma}_n(s)
        \right\}
        [\Lambda - \hat{\Lambda}_n](\diff s)
      \\
      & =
        \int_0^{\tau} w(s) 
        \left\{
        \int_0^s \frac{F(\diff u, 2)}{F(u-, 0)} -
        \int_0^s \frac{\hat{F}_n(\diff u, 2)}{\hat{F}_n(u-, 0)}  -
        \right\}
        \left[
        \frac{F(\diff s, 1)}{F(s-, 0)}
        - \frac{\hat{F}_n(\diff s, 1)}{\hat{F}_n(s-, 0)}
        \right]
      \\
      & =
        \int_0^{\tau} w(s) 
        \Bigg\{
        \int_0^s 
        \left(
        \frac{1}{F(u-, 0)} -  \frac{1}{\hat{F}_n(u-, 0)}
        \right) F(\diff u, 2)
      \\
      & \qquad\qquad \qquad
        +
        \int_0^s \frac{1}{\hat{F}_n(u-, 0)} 
        \left[
        F(\diff u, 2) - \hat{F}_n(\diff u, 2)
        \right]
        \Bigg\}
      \\
      & \qquad\qquad \times
        \left[
        \left(
        \frac{1}{F(s-, 0)} -
        \frac{1}{\hat{F}_n(s-, 0)}
        \right)F(\diff s, 1)
        + \frac{1}{\hat{F}_n(s-, 0)}
        \left(
        F(\diff s, 1) -
        \hat{F}_n(\diff s, 1)
        \right)
        \right]
      \\
      &
        = \int_0^{\tau} 
        \int_0^s
        w(s) 
        \left(
        \frac{1}{F(u-, 0)} -  \frac{1}{\hat{F}_n(u-, 0)}
        \right) 
        \left(
        \frac{1}{F(s-, 0)} -
        \frac{1}{\hat{F}_n(s-, 0)}
        \right)F(\diff u, 2)F(\diff s, 1)
      \\
      & \quad +
        \int_0^{\tau}
        \int_0^s
        w(s) 
        \left(
        \frac{1}{F(u-, 0)} -  \frac{1}{\hat{F}_n(u-, 0)}
        \right) \frac{F(\diff u, 2) }{\hat{F}_n(u-,0)}
        \left(
        F(\diff s, 1) -
        \hat{F}_n(\diff s, 1)
        \right)
      \\
      & \quad +
        \int_0^{\tau} 
        \int_0^s      
        \frac{w(s) }{\hat{F}_n(u-, 0)} 
        \left[
        F(\diff u, 2) - \hat{F}_n(\diff u, 2)
        \right]
        \left(
        \frac{1}{F(s-, 0)} -
        \frac{1}{\hat{F}_n(s-, 0)}
        \right)F(\diff s, 1)
      \\
      & \quad +
        \int_0^{\tau} 
        \int_0^s      
        \frac{w(s) }{\hat{F}_n(u-, 0)} 
        \left[
        F(\diff u, 2) - \hat{F}_n(\diff u, 2)
        \right]
        \frac{1}{\hat{F}_n(s-, 0)}
        \left(
        F(\diff s, 1) -
        \hat{F}_n(\diff s, 1)
        \right).
    \end{align*}
    \endgroup %
    Consider the first term on the right hand side. Defining
  \begin{equation*}
    w_n^*(t)  = 
    \left(
      F(t-, 0)
      - \hat{F}_n(t-, 0)
    \right)
    \left(
      \frac{1}{F(t-, 0)}
      - \frac{1}{\hat{F}_n(t-, 0)}
    \right),
  \end{equation*}
  we can write
  \begin{align*}
    & \int_0^{\tau} 
      \int_0^s
      w(s) 
      \left(
      \frac{1}{F(u-, 0)} -  \frac{1}{\hat{F}_n(u-, 0)}
      \right)      
      \left(
      \frac{1}{F(s-, 0)} -
      \frac{1}{\hat{F}_n(s-, 0)}
      \right)F(\diff u, 2)F(\diff s, 1)
    \\
    & =
      \int_0^{\tau} 
      \int_0^s
      w(s)
      w_n^*(u) 
      \left(
      F(u-, 0) - \hat{F}_n(u-, 0)
      \right)
    \\
    & \qquad \qquad \quad
      \times
      w_n^*(s) 
      \left(
      F(s-, 0) - \hat{F}_n(s-, 0)
      \right)       
      F(\diff u, 2)F(\diff s, 1)
    \\
    & =
      \int_0^{\tau} 
      \int_0^s
      w_n^a(s,u)
      \left(
      F(u-, 0) - \hat{F}_n(u-, 0)
      \right)
      \left(
      F(s-, 0) - \hat{F}_n(s-, 0)
      \right)       
      F(\diff u, 2)F(\diff s, 1),
  \end{align*}
  where we have defined \( w_n^a(s,u) = w(s)w^*_n(s)w^*_n(u) \). By assumption,
  \( w_n^a(s,u) \) is uniformly bounded. The same approach can be applied to the
  three remaining terms which gives the result.
\end{proof}

>>>>

We introduce our notation and framework in Section~\ref{sec:framework}. In
Section~\ref{sec:super-learning} we define general super learning for
right-censored data. Section~\ref{sec:super-learner-simple} introduces the state
learner, and Section~\ref{sec:theor-results-prop} provides theoretical
guarantees. In Section~\ref{sec:targeted-learning} we discuss the use of the
state learner in the context of targeted learning. We report results of our
numerical experiments in Section~\ref{sec:numer-exper} and analyse a prostate
cancer data set in Section~\ref{sec:real-data-appl}.
Section~\ref{sec:discussion} contains a discussion of the merits and limitations
of our proposal. Proofs are given in the Appendix. An implementation of the
state learner is available at \url{https://github.com/amnudn/statelearner} along
with codes for reproducing our numerical experiments.

@@

\begin{proposition}
  \label{prop:stric-prop}
  If \(P_0\in\mathcal{P}\) then
  \begin{equation*}
    F_0 = \argmin_{F \in \mathcal{H}_{\mathcal{P}}} P_0{[\bar{B}_\tau(F, \blank)]},
  % F^* = \argmin_{(\Lambda_1,\Lambda_2,\Gamma) \in \mathcal{M}_{\tau}\otimes\mathcal{M}_{\tau}\otimes\mathcal{M}_{\tau}} P_0{[\bar B_\tau(\phi_{(\Lambda_1,\Lambda_2,\Gamma)}, \blank)]},
  \end{equation*}
  \( H \)-almost surely for any \( j\in \{-1,0,1,2\} \) and almost any
  \( t \in [0, \tau]\).
\end{proposition}
\begin{proof}
  See Appendix~\ref{sec:consistency-proof}.
\end{proof}

@@

\begin{corollary}
  \label{cor:oracle-prop}
  For all \(P_0\in\mathcal{P}\), \( n \in \N \), \( k \in \{1, \dots, K\} \),
  and $\delta>0$,
  \begin{align*}
    \E_{P_0}{\left[ \Vert \hat{\phi}_n(\data_n^{-k}) - F_0 \Vert_{P_0}^2 \right]}
    & \leq (1 + 2\delta)
      \E_{P_0}{\left[ \Vert \tilde{\phi}_n(\data_n^{-k}) - F_0 \Vert_{P_0}^2 \right]}
    \\
    & \quad
      + (1+ \delta) 16   K \tau
      \left(
      13 + \frac{12}{\delta}
      \right)
      \frac{\log(1 + |\mathcal{F}_n|)}{n}.
  \end{align*}
\end{corollary}
\begin{proof}
  See Appendix~\ref{sec:oracle-inequalities}.
\end{proof}

@@

\begin{corollary}
  \label{cor:asymp-cons}
  Assume that \( |\mathcal{F}_n| = \bigO(n^q)\), for some \( q \in \N \) and
  that there exists a sequence \( \phi_n \in \mathcal{F}_n \), \( n \in \N \),
  such that
  \( \E_{P_0}{\left[ \Vert \phi_n(\data_n^{-k}) - F_{0} \Vert_{P_0}^2 \right]} =
  \bigO(n^{-\alpha}) \), for some \( \alpha\leq 1 \).
  \begin{enumerate}[label=(\alph*)]
  \item If $\alpha=1$ then
    \( \E_{P_0}{\left[ \Vert \hat{\phi}_n(\data_n^{-k}) - F_0 \Vert_{P_0}^2
      \right]} = \bigO(\log(n)n^{-1}) \).
  \item If $\alpha<1$ then
    \( \E_{P_0}{\left[ \Vert \hat{\phi}_n(\data_n^{-k}) - F_0 \Vert_{P_0}^2 \right]} =
    \bigO(n^{-\alpha}) \).
  \end{enumerate}
\end{corollary}
\begin{proof}
  See Appendix~\ref{sec:oracle-inequalities}.
\end{proof}

\subsection{Transience of the second order remainder structure}
\label{sec:trans-second-order}

@@

\section{Competing interests}
No competing interest is declared.

@@

\section{Proofs}
\label{sec:proofs}

This section contains proofs of the results stated in the paper.
Section~\ref{sec:consistency-proof} contains a proof of the consistency result
from Section~\ref{sec:consistency}; Section~\ref{sec:oracle-inequalities}
contains proofs of the oracle inequalities from
Section~\ref{sec:finite-sample-oracle}; and
Section~\ref{sec:state-learner-with} demonstrates transience of the second
order remainder structure stated in Section~\ref{sec:trans-second-order}.

% We start by recalling some notation. We use \( F \) to denote a function that
% describes the conditional state occupation probabilities of the observed data,
% as defined in equation~(5) of the main paper. We denote the integrated Brier
% score as \( \bar B_\tau( F,O) = \int_0^{\tau} B_t(F,O) \diff t \), where
% \( B_t \) is defined
% \begin{equation*}
%   B_t(F,O) = \sum_{j=-1}^{2}
%   \left(
%       F(t,j,X) - \1{\{\eta(t)=j\}}
%   \right)^2.
% \end{equation*}
% Finally, recall that we let $\mathcal{H}_{\mathcal{P}}$ denote the function
% space consisting of all conditional state occupation probability functions for
% some measure \( P \in \mathcal{P} \), and that we equipped this space with the
% norm
% \begin{equation}
%   \label{eq:norm}
%   \| F \|_{P_0} = 
%   \left\{
%     \sum_{j=-1}^{2}\int_{\mathcal{X}} \int_0^{\tau} F(t, j, x)^2 \diff t H_0( \diff x)
%   \right\}^{1/2},
% \end{equation}
% for some fixed measure \( P_0 \in \mathcal{P} \). We use \( F_0 \) to denote the
% conditional state occupation probability function associated with the measure
% \( P_0 \).

\subsection{Consistency}
\label{sec:consistency-proof}

Define
\( \bar{B}_{\tau,0}(F, o) = \bar{B}_{\tau}(F, o) - \bar{B}_{\tau}(F_0, o) \) and
\( R_{0}(F) = P_0{[\bar{B}_{\tau,0}(F, \blank)]} \), where the integrated Brier
score \( \bar{B}_{\tau} \) was defined in
Section~\ref{sec:super-learner-simple}.
\begin{lemma}
  \label{lemma:norm}
  \( R_{0}(F) = \Vert F - F_0 \Vert_{P_0}^2 \), where \( \Vert \blank \Vert_{P_0}\) is defined
  in equation~(\ref{eq:norm}).
\end{lemma}
\begin{proof}[Proof]
  For any \( t \in [0, \tau] \) and \( j\in \{-1,0,1,2\} \) we have
  \begin{align*}
    & \E_{P_0}{\left[ (F(t, j, X) - \1{\{\eta(t) = j \}})^2 \right]}
    \\
    & =    \E_{P_0}{\left[ (F(t, j, X) - F_0(t, j, X) + F_0(t, j, X) - \1{\{\eta(t) = j
      \}})^2 \right]}
    \\
    & =    \E_{P_0}{\left[ (F(t, j, X) - F_0(t, j, X))^2\right]}
      + \E_{P_0}{\left[ (F_0(t, j, X) - \1{\{\eta(t) = j \}})^2\right]}
    \\
    & \quad
      + 2\E_{P_0}{\left[ (F(t, j, X) - F_0(t, j, X))(F_0(t, j, X) - \1{\{\eta(t) = j
      \}})\right]}
    \\
    & =    \E_{P_0}{\left[ (F(t, j, X) - F_0(t, j, X))^2\right]}
      + \E_{P_0}{\left[ (F_0(t, j, X) - \1{\{\eta(t) = j \}})^2\right]},
  \end{align*}
  where the last equality follows from the tower property. Hence, using Fubini,
  we have
  \begin{equation*}
    P{[\bar{B}_{\tau}(F, \blank)]}
    = \Vert F - F_0 \Vert_{P_0}^2 + P_0{[\bar{B}_{\tau}(F_0, \blank)]}.
  \end{equation*}
\end{proof}

@@

\subsection{Oracle inequalities}
\label{sec:oracle-inequalities}

Recall that we use \( \mathcal{F}_n \) to denote a library of learners for the
function \( F \), and that \( \hat{\phi} \) and \( \tilde{\phi} \) denotes,
respectively, the discrete super learner and the oracle learner for the library
\( \mathcal{F}_n \), c.f., Section~\ref{sec:super-learner-simple}.

@@

\subsection{Transience of the second order remainder structure}
\label{sec:state-learner-with}

Recall that we let $\Lambda_1$ denote the conditional cumulative hazard function
for one of the event times of interest and $\Gamma$ the conditional cumulative
hazard function for censoring, c.f., Section~\ref{sec:framework}.

\begin{proof}[Proof of Proposition~\ref{prop:dr-structure}]
  For notational convenience we suppress \( X \) in the following. The final
  result can be obtained by adding the argument \( X \) to all functions and
  averaging. We use the relations from equation~\eqref{eq:7} to write
  \begingroup %
  \allowdisplaybreaks
      & \int_0^{\tau} w(s) 
        \Gamma(s) - \hat{\Gamma}_n(s)
        [\Lambda_1 - \hat{\Lambda}_{1,n}](\diff s)
        \int_0^{\tau} w(s) 
        \int_0^s \frac{F(\diff u, -1)}{F(u-, 0)} -
        \int_0^s \frac{\hat{F}_n(\diff u, -1)}{\hat{F}_n(u-, 0)}  -
        \left[
        \frac{F(\diff s, 1)}{F(s-, 0)}
        - \frac{\hat{F}_n(\diff s, 1)}{\hat{F}_n(s-, 0)}
        \right]
        \int_0^{\tau} w(s) 
        \Bigg\{
        \int_0^s 
        \frac{1}{F(u-, 0)} -  \frac{1}{\hat{F}_n(u-, 0)}
        \right) F(\diff u, -1)
      & \qquad\qquad \qquad
        +
        \int_0^s \frac{1}{\hat{F}_n(u-, 0)} 
        \left[
        F(\diff u, -1) - \hat{F}_n(\diff u, -1)
        \right]
        \Bigg\}
      & \qquad\qquad \times
        \left[
        \frac{1}{F(s-, 0)} -
        \frac{1}{\hat{F}_n(s-, 0)}
        \right)F(\diff s, 1)
        + \frac{1}{\hat{F}_n(s-, 0)}
        F(\diff s, 1) -
        \hat{F}_n(\diff s, 1)
        \right]
        = \int_0^{\tau} 
        \int_0^s
        w(s) 
        \frac{1}{F(u-, 0)} -  \frac{1}{\hat{F}_n(u-, 0)}
        \frac{1}{F(s-, 0)} -
        \frac{1}{\hat{F}_n(s-, 0)}
        \right)F(\diff u, -1)F(\diff s, 1)
        \int_0^{\tau}
        \int_0^s
        w(s) 
        \frac{1}{F(u-, 0)} -  \frac{1}{\hat{F}_n(u-, 0)}
        \right) \frac{F(\diff u, -1) }{\hat{F}_n(u-,0)}
        F(\diff s, 1) -
        \hat{F}_n(\diff s, 1)
        \int_0^{\tau} 
        \int_0^s      
        \frac{w(s) }{\hat{F}_n(u-, 0)} 
        \left[
        F(\diff u, -1) - \hat{F}_n(\diff u, -1)
        \right]
        \frac{1}{F(s-, 0)} -
        \frac{1}{\hat{F}_n(s-, 0)}
        \right)F(\diff s, 1)
        \int_0^{\tau} 
        \int_0^s      
        \frac{w(s) }{\hat{F}_n(u-, 0)} 
        \left[
        F(\diff u, -1) - \hat{F}_n(\diff u, -1)
        \right]
        \frac{1}{\hat{F}_n(s-, 0)}
        F(\diff s, 1) -
        \hat{F}_n(\diff s, 1)
        \right).
    \endgroup %
    Consider the first term on the right hand side. By the mean value theorem,
      \frac{1}{F(t-, 0)}
      - \frac{1}{\hat{F}_n(t-, 0)}
      = \frac{-1}{\tilde{r}_n(t)^2}
      \left[
        F(t-, 0)
        - \hat{F}_n(t-, 0)
      \right],
    where \( \tilde{r}_n(t) \) is some value between \( \hat{F}(t-, 0) \) and
    \( \hat{F}_n(t-, 0) \). Letting \( w_n^*(t) = -\tilde{r}_n(t)^{-2} \), we
    may write
    & \int_0^{\tau} 
      \int_0^s
      w(s) 
      \frac{1}{F(u-, 0)} -  \frac{1}{\hat{F}_n(u-, 0)}
      \frac{1}{F(s-, 0)} -
      \frac{1}{\hat{F}_n(s-, 0)}
      \right)F(\diff u, -1)F(\diff s, 1)
      \int_0^{\tau} 
      \int_0^s
      w(s)
      w_n^*(u) 
      F(u-, 0) - \hat{F}_n(u-, 0)
    & \qquad \qquad \quad
      \times
      w_n^*(s) 
      F(s-, 0) - \hat{F}_n(s-, 0)
      F(\diff u, -1)F(\diff s, 1)
      \int_0^{\tau} 
      \int_0^s
      w_n^a(s,u)
      F(u-, 0) - \hat{F}_n(u-, 0)
      F(s-, 0) - \hat{F}_n(s-, 0)
      F(\diff u, -1)F(\diff s, 1),
  where we have defined \( w_n^a(s,u) = w(s)w^*_n(s)w^*_n(u) \). By the
  assumption that \( F(\blank,0) \) and \( F_n(\blank,0) \) are uniformly
  bounded away from zero on \( [0,\tau] \), it follows that \( w_n^* \) is
  uniformly bounded, and hence \( w_n^a(s,u) \) is also uniformly bounded,
  because \( w \) was assumed uniformly bounded. The same approach can be
  applied to the three remaining terms which gives the result.
